### 2015-05-08 paper/paper.Rmd
adjusts the studying-hours section
- adds standard error
- removed histogram

```{r load_packages, echo = FALSE, message = FALSE, warning = FALSE, results='hide'}
library(plyr)
library(dplyr)
library(stringr)
library(reshape2)
library(ggplot2)
library(lubridate)
#library(ggvis)
library(maps)
library(ggmap)
library(htmltools)
library(rworldmap)
library(grid)    
library(scales)
library(doBy)
```

@@

```{r studying, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
student.luke <- student2012[,c("name","PV1MATH","PV1READ","PV1SCIE","ST57Q01")]
#study.luke <- melt(student.luke,id=c("name","ST57Q01"))
studyplot <- ggplot(data = student.luke, aes(ST57Q01, PV1MATH)) + xlab("Hours spent out of school studying per week") + ylab("Math score") + facet_wrap(~name) + stat_smooth(se=F)
studyplot
```

```{r studyingbar, fig.width=4, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
studybar <- ggplot(data = student.luke, aes(ST57Q01) ) + geom_histogram(binwidth=5) + xlab("Hours spent studying")
studybar
```

>>>>

```{r load_packages, echo = FALSE, message = FALSE, warning = FALSE, results='hide'}
library(plyr)
library(dplyr)
library(stringr)
library(reshape2)
library(ggplot2)
library(lubridate)
#library(ggvis)
library(maps)
library(ggmap)
library(htmltools)
library(rworldmap)
library(grid)    
library(scales)
library(doBy)
library("ggsubplot")
```

@@

```{r studying, fig.width=10, fig.height=12, echo = FALSE, message = FALSE, warning = FALSE}
student.luke <- student2012[,c("name","PV1MATH","PV1READ","PV1SCIE","ST57Q01")]
#study.luke <- melt(student.luke,id=c("name","ST57Q01"))
studyplot <- 
  ggplot(
    data = student.luke, 
    aes(x = ST57Q01, y = PV1MATH)
  ) + 
  xlab("Hours spent out of school studying per week") + 
  ylab("Math score") + 
  stat_smooth(se=TRUE) +
  facet_wrap(~name)

studyplot
```

```{r studyingbar, fig.width=4, fig.height=4, echo = FALSE, message = FALSE, warning = FALSE}
# studybar <- ggplot(data = student.luke, aes(ST57Q01) ) + geom_histogram(binwidth=5) + xlab("Hours spent studying")
# studybar
```
